Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-02 draft/paper1_jenny.tex
Edit Discussion 5

%% ------------------------------------------------------------------------------------ %% 
\subsection{Stellar Halo or Intra-cluster Light?}

@@

    The majority of massive galaxies in our samples are not considered as BCGs
    At the imaging depth of HSC, we find no evidence for a clearly distinction between 
    an ``inner component'' and an ``intra-cluster'' component. 
    Instead, most of our profiles are smoothly varying out to 100 kpc with little 
    evidence for a distinct secondary component. 
    We do note however, that our \rbcg{} sample contains only a small fraction of 
    extremely massive clusters where strong evidence of photometric ICL component is 
    often found (\mhalo{}$\simgt 10^{15}M_{\star}$). 
    At the typical \mhalo{} of our \rbcg{} clusters, one good nearby example would be 
    the Virgo cluster, whose ultra-deep images (e.g. \citealt{Mihos2016}) show
    that the stellar halo of the BCG can smoothly extends beyond 100 kpc, while the 
    ICL only becomes important outside that radius and is dominated by individual 
    tidal features.
Reliable isolation of a physically meaningful ICL component using photometry 
    alone is extremely difficult, if not impossible.

>>>>

%% ------------------------------------------------------------------------------------ %% 
\subsection{Stellar Halo and Intra-cluster Light}

@@

    In practice, reliable isolation of a physically meaningful ICL component using 
    photometry alone is extremely difficult, if not impossible. 
    More importantly, he majority of massive galaxies in our samples are not considered 
    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$). 
    Even for BCGs in the \rbcg{} samples, only small fraction of them belong to very 
    massive clusters where strong evidence of photometric ICL component is 
    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
    Burke2015}).
    For typical \rbcg{} cluster in our sample, the Virgo cluster is a good nearby 
    example.  
    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
    100 kpc, while the ICL only becomes important outside that radius and is dominated 
    by many individual tidal features (e.g. \citealt{Mihos2016}).
    Therefore, it is highly unlikely the main results are driven by the ICL component.

    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    has been used as evidence of a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    an integrate component. 
    They both carry important information regarding the assembly of central galaxy 
    and its dark matter halo.
